Verifying Demonstrations

### 2018-10-31 paper/adversary-model.tex
Removes adversary goal from def (now in P1, P2)
moved system model and physical assumptions to system model section. Moved discussion part of assumptions on MANET to limitations. Moved adversary models (the one with many different types) to security analysis as they already contain analysis.
proofread of the paper

\subsection{System, communication and adversary model}%
\label{adversary-model}

We provide one system model with two possible adversaries: one who tries to 
link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
which tries to link a protester's or a witness's real identity (\(P\) 
respectively \(W\)) to a location (\(l\)).
We also define varying strengths of each adversary.

@@

\begin{definition}[Base identity--cause adversary]%
  \label{base-identity-cause-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
  \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), where \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
  The adversary wins if he can link \(\cid\) and \(P\).
\end{definition}

@@

\begin{definition}[Stonger identity--cause adversary]%
  \label{stronger-identity-cause-adversary}
  The situation is the same as in \cref{base-identity-cause-adversary}, but now the 
  witness \(W\) learns the protester \(P\)'s identity.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

@@

The players are still the same, but now the adversary controls other players: 
in particular, the adversary controls only the storage \(S\).

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The adversary controls \(S\).
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{P,W}(P, W, l)\) and the time it took 
  place, \(t_{P,W}\).
  \begin{description}
    \item[The witness case:]
      The witness later communicates with \(S\), where \(S\) only learns 
      \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
      happened, \(t_{W,S}\).
      The adversary wins if he can link \(W\) and \(l\).
    \item[The protester case:]
      The protester later communicates with \(S\), where \(S\) only learns 
      \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 
      happened, \(t_{P,S}\).
      The adversary wins if he can link \(P\) and \(l\).
  \end{description}
\end{definition}

>>>>

\subsection{Adversary models}%
\label{adversary-model-different-levels}

We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
that aims at linking a protester's or a witness's real identity (\(P\), respectively \(W\)), to a location (\(l\)).
We also define varying strengths of each adversary.

@@

\begin{definition}[Base identity--cause adversary]%
  \label{base-identity-cause-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
  \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

@@

\begin{definition}[Stronger identity--cause adversary]%
  \label{stronger-identity-cause-adversary}
  The situation is the same as in \cref{base-identity-cause-adversary}, but now the 
  witness \(W\) learns the protester \(P\)'s identity.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

@@

The players are still the same, but now the adversary controls other players.
In particular, the adversary controls the storage \(S\).

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The adversary controls \(S\).
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{P,W}(P, W, l)\) and the time it took 
  place, \(t_{P,W}\).
  \begin{description}
    \item[The witness case:]
      The witness later communicates with \(S\), in which \(S\) only learns 
      \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
      happened, \(t_{W,S}\).
      The adversary wins if he can link \(W\) and \(l\).
    \item[The protester case:]
      The protester later communicates with \(S\), in which \(S\) only learns 
      \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 
      happened, \(t_{P,S}\).
      The adversary wins if he can link \(P\) and \(l\).
  \end{description}
\end{definition}

### 2018-10-31 paper/privacy-properties.tex
proofread of the paper

In addition to the verification requirements, we also need to define the 
privacy properties.
In voting protocols, there are mainly three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can 
    be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
    the vote was cast in any particular way.
\end{description}

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against 
her will.
Receipt freeness, while desirable, is not \emph{always} desirable.
For instance, the location proof might be useful to prove presence to a third 
party, \eg for strengthening the authenticity of witness information.

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity 
\(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not 
be able to link another proof (\eg, from a different protest) as a consequence.

For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\) against an adversary who is not present in the location.
Due to the limitations of physical space, two individuals present in the same 
location will inevitably learn of each other's presence.
Thus we will only try to prevent individuals who are not present to learn of 
this presence.

\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

Given that all conditions for being counted in a protest are met, individual 
verifiability implies a receipt \daniel{no, I know my proof is included in 
 block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
 sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
 to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
 hence receipt-freeness} because being counted implies support for a cause. 
This also means that besides physical force, coercion can happen by forcing the 
participate to show a receipt. \daniel{The only receipt we have is the private 
 key of the protester, with that key the adversary can compute \(\pid = 
   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
We thus have to decide between individual verifiability and the privacy 
properties for e-voting or define privacy properties suitable for the scenario. 
The ultimate privacy requirement is thus stronger here: in contrast to voting, 
where it is the content of the vote itself that needs to be unlinkable to the 
voter, here the fact of having cast a vote at all needs to be unlinkable.

The privacy properties we need in this context are the following:
\begin{description}
 \item[Involuntary participant unlinkability:] \daniel{the name has a 
     double-negative ring to me} unless the participant discloses the receipt 
   (by revealing her identity), there is no link between the protest data on 
   the ledger and the identity of the participant.

 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
  participant's real (long-term) 
  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
  participation proofs $\prf_{\pid, \prtst}$ must be 
  unlinkable between protests ($\cid, \cid'$)
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
  protesters. ($\pid, \pid'$)
\end{requirements}

\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, is a slight increase in privacy over ordinary protests.}

>>>>

In addition to the verification requirements, we also need to define the privacy properties.
In voting protocols, there are mainly three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove that his vote was cast in any particular way.
\end{description}

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness is not \emph{always} desirable.
For instance, the participation proof might be useful to prove presence to a third party, \eg for strengthening the authenticity of witness information.
%Seb: the above sentence seems to contradict the property of coercion-resistance

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's through some auxiliary knowledge, she should not be able to link another proof (\eg, from a different protest) as a consequence.

For the witness, we want unlinkability between a witness's identity \(W\) and a location \(l\) against an adversary who is not present in the location.
Due to the limitations of physical space, two individuals present in the same location will inevitably learn of each other's presence.
Thus, we will only try to prevent individuals who are not present on the scene to learn this information.

\sonja{new}
To contrast the difference between our context and e-voting: physical presence means support for a cause if there is only one protest. 
In case of a counterprotest, physical presence with that group means support for the counterprotest. 
In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (\ie cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
To summarize, one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.

%Seb: I have put all this part in comment to (1) save on space and (2) also because there is a paper at CCS 2018 that actually shows that individual verifiability is needed to have privacy for e-voting (I agree that it does not mean that it is necessarily the case in our setting) 
%Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt \daniel{no, I know my proof is included in 
% block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
% sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
% to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
% hence receipt-freeness} because being counted implies support for a cause. 
%This also means that besides physical force, coercion can happen by forcing the 
%participate to show a receipt. \daniel{The only receipt we have is the private 
% key of the protester, with that key the adversary can compute \(\pid = 
%   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
%We thus have to decide between individual verifiability and the privacy 
%properties for e-voting or define privacy properties suitable for the scenario. 
%Seb: below I would use the term unobservability, rather than unlinkability
%The ultimate privacy requirement is thus stronger here: in contrast to voting, in which it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.

The privacy properties we need in this context are the following:
\begin{description}
%Seb: while not use the term anonymity instead of unlinkability?
\item[Involuntary participant unlinkability:] \daniel{the name has a 
     double-negative ring to me} unless the participant discloses the receipt 
   (by revealing her identity), there is no link between the protest data on 
   the ledger and the identity of the participant.
%Seb: same comment as above
 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to her participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

%Seb: maybe this sentence should be put before the definition of the properties
As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
  identities must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
  unlinkable between protests and witnesses' proofs must be unlinkable between 
  protesters.
\end{requirements}

As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, a slight increase in privacy over ordinary protests.

### 2018-10-31 paper/system-model.tex
proofread of the paper

To set the stage, we will now describe our system model including assumptions
(\cref{assumptions}) and present an abstraction of a protest and how to
count the participation (\cref{protest-model}). We then formulate the desired verifiability
(\cref{verifiability-properties}) and privacy properties
(\cref{privacy-properties}) and adversary model (\cref{adversary-model}).

@@

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}.

In practical terms, participants witness each other's participation
using their smartphones (or similar devices) running the protocol
described in \cref{Protocol} and uploading their testimony (\ie, proof
shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in
terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is
necessary during this time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie, Internet connections) and are not computationally limited by any battery.
\sonja{another place to put reasons? Or if here, then for all
  assumptions. ``We need global connectivity before to read the head from the blockchain.
We need global connectivity after to upload the proof shares to the blockchain.''}

>>>>

To set the stage, we will now describe our system model including assumptions (\cref{assumptions}) and present an abstraction of a protest and how to
count the participation (\cref{protest-model}). 
Afterwards, we formulate the desired verifiability (\cref{verifiability-properties}) and privacy properties
(\cref{privacy-properties}) as well as the adversary model (\cref{adversary-model}).

@@

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.
%\sonja{another place to put reasons? Or if here, then for all
%  assumptions. ``We need global connectivity before to read the head from the blockchain.
%We need global connectivity after to upload the proof shares to the blockchain.''}
